\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels}

### 2024-01-19 paper/paper.tex
Updates from Overleaf

%=================================================================
% Full title of the paper (Capitalized)
\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels }}

@@

\begin{figure}[H]
\includegraphics[width=10.5 cm]{paper/figures/results/target_correlations.pdf}
\caption{\label{fig:target-correlations}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
\caption{Distribution of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

\begin{table}[H]
  \caption{Summary of fitting statistics for each target measurement. Models were evaluated using 6-fold cross validation on the training set. The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set. The empirical coverage is the percentage of predictions in the testing set that fall within the confidence interval determined by conformal prediction. The final column shows the best performing model. \label{tab:fit-results}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCC}
    \toprule
    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} \\
    \midrule
    Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 \\
    $Conductivity$ & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
    $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 \\
    $\mathrm{Cl^-}$ & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 \\
    Blue-Green Algae (Phycoerythrin) & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 \\
    pH & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 \\
    $\mathrm{Na^+}$ & 0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 \\
    CDOM & 0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 \\
    Crude Oil & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 \\
    Optical Brighteners & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 \\
    $Chlorophyll A$ & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 \\
    Turbidity & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 \\
    Blue-Green Algae (Phycocyanin) & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 \\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}

@@

discuss distribution of values each day and identify variables which had mostly constant values between all three days (and so were highly impaced by the presece of outliers)...

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.png}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the physical parameters we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:physical-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/physical-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three physical parameter models.\label{fig:physical-fit}}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.png}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the ion concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:ions-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/ions-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three ion concentration models.\label{fig:ions-fit}}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the chemical concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.png}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the chemical concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fit}}
\end{figure}

@@

We can probably explain the inference of salinity, ion concentrations, etc as being directly related to the observed concentrations of chlorophyll, cdom, co, bgm, etc... which are all optically active (i.e. have absorption features spectral region of our hyperspectral imager).

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{\textcolor{red}{Leveraging Machine Learning to Characterize Water Quality with an Autonomous Team of Sensing Sentinels}}

@@

\begin{figure}[H]
\includegraphics[width=0.75\columnwidth]{paper/figures/results/target_correlations.pdf}
\caption{\label{fig:target-correlations}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.75\columnwidth]{paper/figures/results/downwelling-hist.pdf}
\caption{Distribution of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

\begin{table}[H]
  \caption{Summary of fitting statistics for each target measurement. Models were evaluated using 6-fold cross validation on the training set. The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set. The empirical coverage is the percentage of predictions in the testing set that fall within the confidence interval determined by conformal prediction. The final column shows the best performing model. \label{tab:fit-results}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCC}
    \toprule
    \textbf{Target} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)} \\
    \midrule
    Temperature & 1.0 ± 6.04e-6 & 0.0289 ± 0.000466 & 0.0162 ± 0.00016 &  ± 0.039 & 90.3 \\
    Conductivity & 1.0 ± 1.54e-5 & 0.574 ± 0.0128 & 0.322 ± 0.00579 &  ± 0.76 & 90.6 \\
    $\mathrm{Ca}^{2+}$ & 1.0 ± 1.06e-5 & 0.285 ± 0.00357 & 0.137 ± 0.00224 &  ± 0.33 & 89.8 \\
    $\mathrm{Cl^-}$ & 0.995 ± 0.000196 & 0.895 ± 0.0202 & 0.516 ± 0.00759 &  ± 1.2 & 90.1 \\
    Blue-Green Algae (Phycoerythrin) & 0.995 ± 0.000601 & 0.783 ± 0.0489 & 0.287 ± 0.00959 &  ± 0.73 & 89.3 \\
    pH & 0.994 ± 0.000288 & 0.0145 ± 0.000304 & 0.00739 ± 9.49e-5 &  ± 0.017 & 89.5 \\
    $\mathrm{Na^+}$ & 0.993 ± 0.000229 & 6.16 ± 0.102 & 2.83 ± 0.0303 &  ± 7.3 & 90.0 \\
    CDOM & 0.965 ± 0.00352 & 0.248 ± 0.0142 & 0.0921 ± 0.0024 &  ± 0.15 & 89.9 \\
    Crude Oil & 0.949 ± 0.00267 & 0.247 ± 0.00597 & 0.0935 ± 0.00114 &  ± 0.17 & 89.8 \\
    Optical Brighteners & 0.943 ± 0.00122 & 0.0806 ± 0.0014 & 0.0481 ± 0.000416 &  ± 0.095 & 89.8 \\
    $Chlorophyll A$ & 0.908 ± 0.00664 & 0.37 ± 0.00934 & 0.131 ± 0.00228 &  ± 0.27 & 89.2 \\
    Turbidity & 0.897 ± 0.00611 & 3.13 ± 0.084 & 0.736 ± 0.0156 &  ± 1.1 & 89.8 \\
    Blue-Green Algae (Phycocyanin) & 0.708 ± 0.00689 & 0.749 ± 0.0129 & 0.446 ± 0.00405 &  ± 0.93 & 89.8 \\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}

@@

For each type, discuss:
- Data Distribution (unimodal, multimodal, spatial variability within each day)
- Fit results (parameter regions where performance is poor)
- Feature importance rankings 
- Maps
- Can we explain the quality of fit? e.g. target is optically active, correlates with an optically active substance, or has some other physical explanation

\begin{figure}[H]
%\begin{adjustwidth}{-\extralength}{0cm}
\centering
%\includegraphics[width=16.0cm]{paper/figures/results/fits/biochemical-fitres.png}
\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-fitres.pdf}
%\end{adjustwidth}
\caption{Scatter plots (left) and quantile-quantile plots (right) for the final hyperparameter optimized models for the biochemical targets Blue-green algae (phycoerythrin), CDOM, Chlorophyll-A, and Blue-green algae (phycocyanin). \label{fig:biochem-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/biochemical-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:biochem-fi}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/chemical-fitres.pdf}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the chemical concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:chemicals-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/chemical-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three chemical concentration models.\label{fig:chemicals-fi}}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/physical-fitres.pdf}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the physical parameters we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:physical-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/physical-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three physical parameter models.\label{fig:physical-fi}}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=16.0cm]{paper/figures/results/fits/ions-fitres.pdf}
\end{adjustwidth}
\caption{A visualization of the fitresults for three of the ion concentrations we modeled. On the left is a scatterplot and on the right is plot of the associated quantiles.\label{fig:ions-fit}}
\end{figure}

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18.0cm]{paper/figures/results/fits/ions-ranking.pdf}
\end{adjustwidth}
\caption{Ranked feature importances for the same three ion concentration models.\label{fig:ions-fi}}
\end{figure}

@@

@@
